Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-03-19 analysis2_manuscript.tex
Update analysis2_manuscript.tex
Co-authored-by: Andrew Kern <adkern@uoregon.edu>

    Although the estimates produced by the four methods differ from one another, 
    for each method the estimates produced from data with selection (Figure
    \ref{fig:human-demography}; orange) and without selection (Figure
    \ref{fig:human-demography}; blue) are fairly similar.
    Thus, this particular parameterization of background selection and demographic model,
    in combination with selection only at exonic sites, %in the out-of-Africa demographic model IG: it's probably not just this specific demo model
    does not appear to notably bias the estimates produced by these methods.
    This makes sense in light of our observation that genetic diversity is mostly affected
    within exonic regions and presumably sites very closely linked (Figure \ref{fig:homsap-summary-stats}),
    thus masking of exons should be sufficient to remove the major effects of selection. 
    As noted in previous studies that compared demographic inference methods
    on neutral simulations \citep{adrion2020community},
    we see that each method has its strengths and weaknesses.
    Methods based on the sequential Markovian coalescent (\smcpp and \msmc)
    appear to produce the most accurate trajectories of $N_e(t)$ overall
    in this setting, although they tend to under-estimate the population
    bottleneck associated with the population split.
    On the other hand, \stairway, which utilizes the site frequency spectrum,
    produces more noisy estimates,
    but it does not appear to under-estimate the population bottleneck.
    The inference of \gone, which utilizes identity by descent,
    is targeted toward demographic changes in more recent time frames ($\sim 200$ generations),
    explaining its noisy estimates for all but the most recent time periods.

>>>>

    Although the estimates produced by the four methods differ from one another, 
    for each method the estimates produced from data with selection (Figure
    \ref{fig:human-demography}; orange) and without selection (Figure
    \ref{fig:human-demography}; blue) are fairly similar.
    Thus, this particular parameterization of background selection and demography,
    in combination with selection only at exonic sites, %in the out-of-Africa demographic model IG: it's probably not just this specific demo model
    does not appear to notably bias the estimates produced by these methods.
    This makes sense in light of our observation that genetic diversity is mostly affected
    within exonic regions and presumably sites very closely linked (Figure \ref{fig:homsap-summary-stats}),
    thus masking of exons should be sufficient to remove the major effects of selection. 
    As noted in previous studies that compared demographic inference methods
    on neutral simulations \citep{adrion2020community},
    we see that each method has its strengths and weaknesses.
    Methods based on the sequential Markovian coalescent (\smcpp and \msmc)
    appear to produce the most accurate trajectories of $N_e(t)$ overall
    in this setting, although they tend to under-estimate the population
    bottleneck associated with the population split.
    On the other hand, \stairway, which utilizes the site frequency spectrum,
    produces more noisy estimates,
    but it does not appear to under-estimate the population bottleneck.
    The inference of \gone, which utilizes identity by descent,
    is targeted toward demographic changes in more recent time frames ($\sim 200$ generations),
    explaining its noisy estimates for all but the most recent time periods.
